Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
b

For each listed property, 34 features and the target variable (price) was collected. Appendix \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	

@@

\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction \\	

@@

\paragraph{DAWA\newline}
\href{https://dawa.aws.dk/}{Denmark's Addresses Web API}\footnote{red. Danmarks Adressers Web API} (DAWA) is an API containing data regarding Danish addresses. DAWA will be used to collect information about the municipality that each address is located in. This data will be used to merge the socio-demographic data collected from various sources (see below) with the data scraped from Boliga.

@@

\subsubsection{Property Type}
Another worthwhile consideration is that we have included all types of properties. It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property. Figure 4 displays the median valuation price for each type:
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[scale=0.5]{bar1.png} 
  \label{fig:}
\end{figure}
It is interesting to note that the most expensive properties are apartments as opposed to houses. This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing. Refraining from delving deeper into a discussion of global urbanisation, we retain the fact that property type does have an effect on average valuation. We will include the ‘type’ feature in our impending model training to control for this effect.

@@

A list of the excluded features is found in appendix 11.0.1. The model used for ML is found in appendix 11.0.2.  
The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularisation yields: 
\begin{table}[H]
\begin{center}
\caption{Optimal hyperparameters, two degrees polynomial features\label{time}}
\begin{tabular}{ c | c  c  c } 
  & $\lambda_{LASSO}$ & $\lambda_{RIDGE}$ \\ \hline
2 degrees  & 372.76 & 22.76 \\ \hline
3 degrees  & 2310.13 & 432.88
\end{tabular}
\end{center}
\end{table}

The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
\begin{table}[H]
\begin{center}
\caption{Prediction Errors. \label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
   LASSO 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
  RIDGE 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
  LASSO 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
  RIDGE 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
  OLS 3-deg & 2.848e+28 & 1.687e+14 & 2.637e+12  \\ \hline
\end{tabular}
\end{center}
\end{table}
Since our efforts are aimed at predicting the valuation of a out-of-sample real estate property, we want to penalise the size of the error. Hence, the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE). Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.

From table 4 it is evident that the model with 3 degrees of polynomial features regularised by RIDGE regression performs best. Figure 11 shows a plot of the predicted values of our model against the actual values of the test data.

@@

\section{Conclusion}
In this research paper we have used machine learning to train a model to predict valuation prices of real estate in Denmark. The model train on sociodemographic and geographical data. \newline We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanisation. Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping. 
We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it. \newline
We performed descriptive statistics to gain a better acquaintance with the data. 
We conducted feature selection by assessing the correlation between the different features and the target variable, which in our research has been the valuation price. 
We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression. Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularisation models. We found that the RIDGE regression with three polynomial features performed best, at predicting out-of-sample data with the performance measure being the smallest mean square error. When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance. 
We have assessed the final model and examined to which degree we have managed to find a good bias-variance trade-off for our model and concluded that our model suffers from a degree of overfitting. This was done by examining the validation- and learning curve of our final model. Additionally we addressed possibilities of further optimising the model.  \newline
Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.

@@

Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]\newline

European Commission (2018). \textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019] \newline

@@

Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline

@@

https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741 [Accessed 27/08/2019]\newline
\newpage
\section{Appendix}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\newpage
\subsubsection{t}

>>>>

For each listed property, 34 features and the target variable (price) was collected. Appendix 9.0.3 provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train, bus\_stop \\	

@@

\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction, s-train, airport \\	

@@

\paragraph{DAWA\newline}
\href{https://dawa.aws.dk/}{Denmark's Addresses Web API}\footnote{red. Danmarks Adressers Web API} (DAWA) is an API containing data regarding Danish addresses. DAWA will be used to collect information about the municipality that each address is located in. This data will be used to merge the sociodemographic data collected from various sources (see below) with the data scraped from Boliga.

@@

\subsubsection{Property Type}
Another worthwhile consideration is that we have included all types of properties. It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property. Figure 9 displays the median valuation price for each type:
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[scale=0.5]{bar1.png} 
  \label{fig:}
\end{figure}
It is interesting to note that the most expensive properties are apartments as opposed to houses. This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing. Refraining from delving deeper into a discussion of global urbanisation, we retain the fact that property type does have an effect on average valuation. We will include the ‘type’ feature in our impending model training to control for this effect.

@@

A list of the excluded features is found in appendix 9.0.1. The model used for ML is found in appendix 9.0.2.  
The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularisation yields: 
\begin{table}[H]
\begin{center}
\caption{Optimal hyperparameters, two degrees polynomial features\label{time}}
\begin{tabular}{ c | c  c  c } 
  & $\lambda_{LASSO}$ & $\lambda_{RIDGE}$ \\ \hline
2 degrees  & 372.76 & 22.76 \\ \hline
3 degrees  & 2310.13 & 432.88
\end{tabular}
\end{center}
\end{table}

The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
\begin{table}[H]
\begin{center}
\caption{Prediction Errors. \label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
   LASSO 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
  RIDGE 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
  LASSO 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
  RIDGE 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
  OLS 3-deg & 2.848e+28 & 1.687e+14 & 2.637e+12  \\ \hline
\end{tabular}
\end{center}
\end{table}
Since our efforts are aimed at predicting the valuation of a out-of-sample real estate property, we want to penalise the size of the error. Hence, the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE). Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim. \newline
From table 4 it is evident that the model with 3 degrees of polynomial features regularised by RIDGE regression performs best. Figure 11 shows a plot of the predicted values of our model against the actual values of the test data.

@@

\section{Conclusion}
In this research paper we have used machine learning to train a model to predict valuation prices of real estate in Denmark. The model train on sociodemographic and geographical data. \newline We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanisation. Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping. 
We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it. \newline
We performed descriptive statistics to gain a better acquaintance with the data. 
We conducted feature selection by assessing the correlation between the different features and the target variable, which in our research has been the valuation price. 
We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression. Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularisation models. We found that the RIDGE regression with three polynomial features performed best, at predicting out-of-sample data with the performance measure being the smallest mean square error. When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance. 
We have assessed the final model and examined to which degree we have managed to find a good bias-variance trade-off for our model and concluded that our model suffers from a degree of overfitting. This was done by examining the validation- and learning curve of our final model. Additionally we addressed possibilities of further optimising the model.  \newline
Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement. In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark

@@

Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \newline\href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020} [Accessed on 25/08/2019]\newline

European Commission (2018). \textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities} [Accessed on 25/08/2019] \newline

@@

Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline

@@

https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741 [Accessed 27/08/2019]\newline
\newpage
\section{Appendix}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\newpage
\subsubsection{}  
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Feature} & \textbf{Description} & \textbf{Dropped} \\ 
\hline 
agentDisplayName & Real estate Agent Name & True \\ 
\hline 
agentRegId & Real-estate Agent ID & True \\ 
\hline 
area & Area of country (11 areas) & True \\ 
\hline 
basementSize & Square meters of basement & False \\ 
\hline 
buildYear & Year of house built & False \\ 
\hline 
city & City Name & False \\ 
\hline 
createdDate & Day of offer creation & True \\ 
\hline 
daysForSale & Scraping date - createdDate & False \\ 
\hline 
domainId & Description unknown & True \\ 
\hline 
energyClass & Energy scale - not sufficiently formated & True \\ 
\hline 
exp & Property expenses & False \\ 
\hline 
floor & Entrance floor & False \\ 
\hline 
groupKey & Key for same buildings & True \\ 
\hline 
guid & Link & True \\ 
\hline 
id & Unique identifier & True \\ 
\hline 
images & Image format dictionary & True \\ 
\hline 
inWatchlist & In profile's watchlist & True \\ 
\hline 
isActive & If the offer is active on webpage (all are active)
 & True \\ 
\hline 
isForeclosure & The house is being foreclosed & True \\ 
\hline 
isPremiumAgent & An agent ranking & True \\ 
\hline 
latitude & Latitude of address & False \\ 
\hline 
longitude & Longitude of adress & False \\ 
\hline 
lotSize & Size of total property & False \\ 
\hline 
municipality & Municipality code & False \\ 
\hline 
net & Description unknown & True \\ 
\hline 
openHouse & Boolean. True if future open house date exists & True \\ 
\hline 
price & Total price (Target) & False \\ 
\hline 
priceChangePercentTotal & Price change since first valuation & True \\ 
\hline 
propertyType & Property type category & False \\ 
\hline 
rooms & No. of rooms & False \\ 
\hline 
selfsale & Bool if property sold without agen & True \\ 
\hline 
size & Size of residential property & False \\ 
\hline 
squaremeterPrice & Price/size & True \\ 
\hline 
street & Street name & True \\ 
\hline 
views & No. of views on website & True \\ 
\hline 
zipCode & Zipcode (Post nr.) & True \\ 
\hline 
\end{tabular}
